A generalized definition of multidimensional item response theory parameters

### 2023-02-17 output/paper_draft/paper_M2PLM_parameters.Rmd
Puts the product of norms (of the unitary vector and the theta vector) always in the same order, and explicitly states that the inner product is in basis B

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each basis,
$`r LS_BASIS`$ or $`r LS_STD_BASIS`$.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$. From now on we  will note  $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

@@

OBS. En la ecuación debe estar el producto inteno con el subindice que indique que es en la base B. No se ponen en las normas debido a la invarianza de estas. Como $\theta$ son las coordanadas en B se dejan igual.

@@

OBS en esta primera ecuación recordar poner el subindice B en el producto interno

>>>>

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each basis,
$`r LS_BASIS`$ or $`r LS_STD_BASIS`$.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$.
From now on, we denote $`r TRAIT_COORDS_EQ`$ and $`r TRAIT_COORDS_STD_EQ`$.

@@

@@
